### 2016-06-09 thesis_paper/source.tex
thesis stuff

@@

\begin{figure}
 \centerline{\includegraphics[width=0.7\columnwidth]{images/chart_max}}
 \caption{Speedup for larger number of atoms}
 \label{fg:chart_max}
\end{figure}

>>>>

\subsection{Advanced SDH implementation}

We implemented more advanced version of SDH algorithm taking better use of shared memory just to demonstrate what improvement and speedup could be achieved if we focus on particular query implementation.

\begin{figure}
 \centerline{ \includegraphics[width=0.3\columnwidth]{images/improved_sdh}}
 \caption{New approach of using shared memory}
 \label{fg:improved_sdh}
\end{figure}

Basically, as you can see from Figure \ref{fg:improved_sdh}, now we allocate more shared memory. Yellow sections are the atoms that are stored in shared memory throughout the whole thread execution of the entire block, since those atoms are needed at every step, while the green ones are the working zones. We load twice size of the block into shared memory, because the very first one thread in the block is going to communicate starting from second one, while the last one will start with the next block, which means that it will have to be twice size. Fortunately, the first part of the threads in the block will consequently use the next block which is already loaded, thus, at each step we load one more block size simply moving window and re-using the ones that are already loaded for first part.

$Duration $ & $ Grid Size $ & $ Block Size $ & $ DSMem* $ & $ Size $ & $ Throughput $ \\ \hline 
$1.4080us $ & $ - $ & $ - $ & $ - $ & $ 4B $ & $ 2.8409MB/s $ \\ \hline 
$1.0769ms $ & $ - $ & $ - $ & $ - $ & $ 3.6000MB $ & $ 3.3429GB/s $ \\ \hline 
$1.0880us $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 33.088MB/s $ \\ \hline 
$1.2800us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 1.1000GB/s $ \\ \hline 
$3.0340ms $ & $ (98, 1, 1) $ & $ (1024, 1, 1) $ & $ 40.960KB $ & $ - $  & $-$ \\ \hline 
$24.5691s $ & $ (98, 1, 1) $ & $  (1024, 1, 1) $ & $ 38.272KB $ & $ - $ & $ - $ \\ \hline 
$2.7520us $ & $ - $ & $ - $ & $ - $ & $ 36B $ & $ 13.081MB/s $ \\ \hline 
$2.7830us $ & $ - $ & $ - $ & $ - $ & $ 1.4080KB $ & $ 505.93MB/s $    
 \\ \hline

	\hline
  \end{tabular}
    \caption{Memory profiling results for 100,000 atoms in improved SDH}
    	  \label{tb:gpumem100000_improved}
\end{table}

\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline
	Device & Context & Stream & Kernel & Warps Launched & Shared Load \\ \hline
	GRID K520 (0) & 1 & 13 & ${gpu\_one\_body\_function}$ & 3136 & 196 \\ \hline
	GRID K520 (0) & 1 & 14 & ${gpu\_two\_body\_function}$ & 3136 & 246,323,337 \\ \hline

  \end{tabular}
    \caption{GPU profiling results for 100,000 atoms for improved SDH}
    	  \label{tb:gpuprofile100000}
\end{table}

\begin{figure}
 \centerline{ \includegraphics[width=0.5\columnwidth]{images/sdhvsimproved}}
 \caption{Comparison of GPU SDH with GPU SDH Improved}
 \label{fg:gpusdhsdh}
\end{figure}

As you may have noticed, even though we increased utilization of shared memory, number of loads is around the same. The trick is that we replaced atoms in shared memory with simpler data structure called $coordinates$ that would contains 3 float type variables which saves huge amount of memory. The results that we have achieved are extremely great, in general all the run times get twice less in comparison with simple SDH approach. You may observe run times for some sample data sets on Figure \ref{fg:gpusdhsdh}. In general, it is quite visible that it is twice less. 
This is a sample improvement which proves that a little more elaboration on a particular query can bring much better results which could end up saving scientists days and months of time of computation.

@@

\begin{figure}
 \centerline{\includegraphics[width=0.8\columnwidth]{images/overall_speedup}}
 \caption{Speedup for larger number of atoms}
 \label{fg:chart_max}
\end{figure}

With improved version of SDH speedup gets up to more than 75 times (Figure \ref{fg:chart_max}). We believe that these numbers could get even better depending on queries and elaboration of improvement of particular cases.
